Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-01 ms.tex
initial comments from Dustin

\author{Aaron M. Meisner\altaffilmark{1,2}}
\author{Dustin Lang\altaffilmark{3}}
\author{David J. Schlegel\altaffilmark{2}}

\altaffiltext{1}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, 
USA}
\altaffiltext{2}{Lawrence Berkeley National Laboratory, Berkeley, CA, 94720, 
USA}
\altaffiltext{3}{Department of Astronomy \& Astrophysics and Dunlap Institute, 
University of Toronto, Toronto, ON M5S 3H4, Canada}

@@

However, until now, no full-sky set of W1/W2 coadds combining all pre and post 
reactivation exposures has existed. The primary motivation for such a data 
product is the enhanced infrared depths achieved, which, among
other benefits, will improve the utility of WISE in selecting higher-redshift 
spectroscopic targets, in particular for the upcoming Dark Energy Spectroscopic
Instrument \citep[DESI,][]{desi}. Additionally, folding in two additional scans
of WISE data at each sky location allows time-dependent artifacts to be nulled,
largely eliminating spatial nonuformities in image quality and derivative 
catalogs.

@@

Here we present a new set of full-sky coadds generated by
combining all publicly available W1/W2 exposures from the AllWISE and NEOWISER
programs, using an adaptation of the \cite{lang14} unWISE methodology. These 
`full-depth' coadds are publicly available online\footnote{http://unwise.me}.

@@

We desired a photometic calibration with time resolution of one day. To
achieve this, we grouped our single-exposure aperture photometry measurements 
in two ways. First, for each 
unique source, we lumped all of its All-Sky phase measurements together to 
obtain its median flux (DN) in our aperture photometry system during this 
phase. This is justified because the All-Sky release photometric zero points 
are known to be remarkably stable \citep{jarrett11}. Indeed, using our ecliptic
pole singe-exposure photometry database, we were able to confirm that the 
All-Sky phase zero point was stable at the $\le$2 mmag level in both bands. 
Next, for every aperture flux after the All-Sky phase, we calculated a 
multiplicative enhancement factor
implied by the ratio of that measurement to the appropriate source's
median All-Sky phase flux. We then grouped these 
multiplicative enhancement factors into one-day bins, and quote the median per 
bin as the change in multiplicative
image scaling relative to the All-Sky zero point. For the  
All-Sky phase zero points, we adopted the \verb|MAGZP| values of 20.752 in W1 
and 19.596 in W2.

@@

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=moon_3433p000.eps, width=6.5in}
  \caption{\label{fig:moon_3433p000} Tile 3433p000, a 
           1.5$^{\circ}$$\times$1.5$^{\circ}$ region of sky at low
           ecliptic latitude which experienced strong Moon contamination 
           during the AllWISE mission phase. Rejecting Moon-contaminated
           frames as described in \ref{sec:moon} while including
           two extra visits worth of NEOWISER data has dramatically
           improved the background level uniformity relative to the
           \cite{lang14} version of this tile. For this tile, we were
           able to recover 58\% (18\%) of frames in W1 (W2).}
 \end{center}
\end{figure*}

In the \cite{lang14} unWISE processing, no steps were taken specifically
to mitigate Moon contamination in W1 and W2. However \cite{lang14} did 
address Moon contamination in W3 and W4. \cite{lang14}
inspected all W3/W4 exposures flagged with the \verb|MOON_MASKED| bit, and 
discarded those frames with abnormally large pixel value standard deviations,
indicative of a strongly varying background level (see \cite{lang14} $\S$2
for full details). In the present work we have applied this same
Moon rejection criterion to W1 and W2 frames. Because of the added redundancy
of two extra NEOWISER scans, we are thus able to reject many W1/W2
frames which are contaminated by moonlight, while still retaining 
sufficient uncontaminated coverage everywhere on the sky to avoid leaving
any holes in the stacks.

@@

Although the present analysis constituted a significant data processing 
endeavor, it represents only a small fraction of the work that must
be done to maximize science return from the NEOWISER imaging data set.
Creation of time-resolved coadds spanning the $\sim$5 year AllWISE-NEOWISER
time baseline would enable a wealth of important time-domain projects,
ranging from brown dwarf searches to IR quasar variability studies. As
additional years worth of NEOWISER data become publicly available, it
will be necessary to continue updating the full-depth AllWISE+NEOWISER coadds
to maximize the achieved W1/W2 depths. Finally, the creation WISE-only (as 
opposed to forced photometry) catalogs based on deep coadds which incorporate
NEOWISER images will be needed to enable a variety of exciting
discoveries.

@@

% cite software packages such as numpy, scipy, matplotlib ??
% mention idlutils

>>>>

\author{Aaron M. Meisner\altaffilmark{1,2}}
\author{Dustin Lang\altaffilmark{3,4}}
\author{David J. Schlegel\altaffilmark{2}}

\altaffiltext{1}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, 
USA}
\altaffiltext{2}{Lawrence Berkeley National Laboratory, Berkeley, CA, 94720, 
USA}
\altaffiltext{3}{Department of Astronomy \& Astrophysics and Dunlap Institute, 
University of Toronto, Toronto, ON M5S 3H4, Canada}
\altaffiltext{4}{Department of Physics \& Astronomy, University of Waterloo,
200 University Avenue West, Waterloo, ON, N2L 3G1, Canada}

@@

However, until now, no full-sky set of W1/W2 coadds combining all pre and post 
reactivation exposures has existed. The primary motivation for such a data 
product is the enhanced infrared depths achieved, which, among
other benefits, will improve the utility of WISE in selecting higher-redshift 
spectroscopic targets, in particular for the upcoming Dark Energy Spectroscopic
Instrument \citep[DESI,][]{desi}. Furthermore, folding in two additional scans
of WISE data at each sky location allows time-dependent artifacts to be nulled,
largely eliminating spatial nonuniformities in image quality and derivative 
catalogs.

@@

Here we present a new set of full-sky coadds generated by
combining all publicly available W1/W2 exposures from the AllWISE and NEOWISER
programs, using an adaptation of the \cite{lang14} unWISE methodology. These 
`full-depth' coadds are publicly available online.\footnote{http://unwise.me}

@@

We desired a photometic calibration with time resolution of one day. To
achieve this, we grouped our single-exposure aperture photometry measurements 
in two ways. First, for each 
unique source, we lumped all of its All-Sky phase measurements together to 
obtain its median flux (DN) in our aperture photometry system during this 
phase. This is justified because the All-Sky release photometric zero points 
are known to be remarkably stable \citep{jarrett11}. Indeed, using our ecliptic
pole single-exposure photometry database, we were able to confirm that the 
All-Sky phase zero point was stable at the $\le$2 mmag level in both bands. 
Next, for every aperture flux after the All-Sky phase, we calculated a 
multiplicative enhancement factor
implied by the ratio of that measurement to the appropriate source's
median All-Sky phase flux. We then grouped these 
multiplicative enhancement factors into one-day bins, and quote the median per 
bin as the change in multiplicative
image scaling relative to the All-Sky zero point. For the  
All-Sky phase zero points, we adopted the \verb|MAGZP| values of 20.752 in W1 
and 19.596 in W2.

@@

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=moon_3433p000.eps, width=6.5in}
  \caption{\label{fig:moon_3433p000} Tile 3433p000, a 
           1.5$^{\circ}$$\times$1.5$^{\circ}$ region of sky at low
           ecliptic latitude which experienced strong Moon contamination 
           during the AllWISE mission phase. Rejecting Moon-contaminated
           frames as described in $\S$\ref{sec:moon} while including
           two extra visits worth of NEOWISER data has dramatically
           improved the background level uniformity relative to the
           \cite{lang14} version of this tile. For this tile, we were
           able to recover 58\% (18\%) of frames in W1 (W2).}
 \end{center}
\end{figure*}

In the \cite{lang14} unWISE processing, no steps were taken specifically
to mitigate scattered moonlight in W1 and W2. However, that analysis did 
address Moon contamination in W3 and W4. \cite{lang14}
inspected all W3/W4 exposures flagged with the \verb|MOON_MASKED| bit, and 
discarded those frames with abnormally large pixel value standard deviations,
indicative of a strongly varying background level (see \cite{lang14} $\S$2
for full details). In the present work we have applied this same
Moon rejection criterion to W1 and W2 frames. Because of the added redundancy
of two extra NEOWISER scans, we are thus able to reject many W1/W2
frames which are contaminated by moonlight, while still retaining 
sufficient artifact-free coverage everywhere on the sky to avoid leaving
any holes in the stacks.

@@

Although the present analysis constituted a significant data processing 
endeavor, it represents only a small fraction of the work that must
be done to maximize science return from the NEOWISER imaging data set.
Creation of time-resolved coadds spanning the $\sim$5 year AllWISE-NEOWISER
time baseline would enable a wealth of important time-domain projects,
ranging from brown dwarf searches to IR quasar variability studies. As
additional years of NEOWISER data become publicly available, it will be 
necessary to continue updating the full-depth AllWISE+NEOWISER coadds to 
maximize the achieved W1/W2 depths. Finally, the creation of WISE-only (as 
opposed to forced photometry) catalogs based on deep coadds which incorporate
NEOWISER images will be needed to enable a variety of exciting discoveries.

@@

% cite software packages such as numpy, scipy, matplotlib ??
